Mapping Properties of Surface Source Extension

### 2025-04-11 repro/papers/ssefound/paper.tex
various

\section{Local Analysis of Surface Source Field}
$k \times  k$ symmetric hyperbolic system: in $\bR^{n+1}$. Suppose that $u \in L^2_{\rm loc}(\bR^{n+1},\bR^k)$ is a weak solution of
\begin{equation}
  \label{eqn:shs}
  (\sum_{i=0}^n A_i\partial_i ) u \in L^2_{\rm loc}(\bR^{n+1},\bR^k)
\end{equation}
The coefficieent matrices $A_i \in C^{\infty}(\bR^n, \bR^{k \times
  k}), i=0,...,n$ are symmetric, $A_0$ is positive definite.

Notation:$x_0=t$, $\partial_t=\partial_0$, $\bx = (x_1,...,x_{n-1})$,
$\partial_x=(\partial_1,...\partial_{n-1})$, $x_n=z$, $\partial_z =
\partial_{n}$, $M=A_0(\bx)$, $A = (A_1,...,A_{n-1}$, $L=A_{n}$.

Asymptotic solution 
\[
u(t,\bx,z) \approx e^{i\omega(t + \psi(\bx,z))} U(\bx,z)\sum_{n=0}^{\infty}
a_n(t,\bx,z)
\]
Substitute first term in equation \ref{eqn:shs}, obtain
\[
(M\partial_t + A\cdot \partial_x + L \partial_z)u(t,\bx,z) =
\]
\[
 e^{i\omega(t + \psi(\bx,z))}\left[ i\omega (M + A
\cdot \partial_x \psi(\bx,z) + L \partial_z
\psi(t,\bx,z))U(\bx,z)a_0(t,\bx,z) \right.
\]
\[
\left. + M(\bx,z) U(\bx,z) \partial_t a_0(t,\bx,z) + \partial_x
(a_0(t,\bx,z) U(\bx,z))\cdot A + L\partial_z (a_0(t,\bx,z)U(\bx,z))\right]= 0
\]
Assume $\Gamma$ is an open neighborhood of $0$ in $\bR^{n-1}$, $Z>0$ so that for each
$\xi \in \Gamma, |\xi|=1$ and $|z| < Z$, there are $l$ independent
solutions
$(\zeta_1(\bx,z,\xi),U_1(\bx,z,\xi)),...,(\zeta_l(\bx,z,\xi), U_l(\bx,z,\xi))$ of
\[
 (M(\bx,z) + A\cdot \xi + L \zeta) U=0.
\]
The $U$s are orthogonal, and might as well normalize by
$|U|=1$. For each $\xi \in \Gamma$, construct by method of characteristics solutions
$\psi_1,...,\psi_l$ of 
\[
\partial_z \psi_i(\bx,z,\xi) = \zeta_i(\bx,z,\partial_x\psi(\bx,z,\xi))
\]
with $\psi_l(\bx,0,\xi) =\xi \cdot x$. The corresponding Hamiltonian
system for $(\bx_i(z;\bx_0,\xi_0),\xi_i(z;\bx_0,\xi_0))$ with
$(\bx_0,\xi_0) \in \Gamma$ is
\begin{equation}
  \label{eqn:zetahe1}
  \frac{d\bx_i}{dz} = - \partial_{\xi}\zeta_i(\bx_i,z,\xi_i),\,
  \bx_i(0;\bx_0,\xi_0) = \bx_0;
\end{equation}
\begin{equation}
  \label{eqn:zetahe2}
  \frac{d\xi_i}{dz}
  = \partial_x\zeta_i(\bx_i,z,\xi_i),\, \xi_i(0;\bx_0,\xi_0) = \xi_0.
\end{equation}
and
\[
  \psi_l(\bx_i(z;\bx_0,\xi_0),z,\xi_i(z;\bx_0,\xi_0))= \bx_0\cdot\xi_0
\]
\begin{equation}
  \label{eqn:psihe}
- \int_0^z ds \xi(s;\bx_0,\xi_0)\cdot \partial_{\xi}\zeta_i(\bx_i(s;\bx_0,\xi_0),s,\xi_i(s;\bx_0,\xi_0))
\end{equation}

$\Pi_0$ = projection on null space $V_0$ of $M(t,\bx)$, $\Pi_1=I-\Pi_0$ = projection on range $V_1$. Denote the rank of $M$ by $l={\rm dim} V_1$ Then

% Suppose that $\Gamma_0, \Gamma \subset T^*(\bR^n)$ are conic open sets with $\overbar{\Gamma_0 \subset \Gamma$ and $\delta t >0$. Assume that  that for $|t|\le \delta t$ and $(\bx,\xi) \in Gamma$, $K_{00}(0,\bx,\xi)$ is invertible as a map $V_0 \rightarrow V_0$.
Let  $L_{00}(t,\bx,\xi) \in C^{\infty}(\bR, S^{-1}(\bR^n))$ be inverse to $K_{0,0}(t,\bx,\xi)$ on $V_0$: that is,
\[
  K_{0,0}(t,\bx,\xi)L_{0,0}(t,\bx,\xi) v=v=L_{0,0}(t,\bx,\xi)K_{0,0}(t,\bx,\xi)v
\]
for all $v \in V_0$. Construct $L_{0,0}$ to be homogeneous of degree -1 outside of a neighborhood of $\xi=0$, with $V_1$ an invariant subspace for $L_{0,0}(t,\bx,\xi)$ on which it vanishes. It follows that $L_{0,0}$ is symmetric, and that
\[
  \Pi_0 u - L_{0,0}K_{0,0}\Pi_u = \Pi_0 u - L_{0,0}K_{0,0}u = \Pi_0 u + L_{0,0}K_{0,1}u \in H^{1}_{\rm loc}(\bR^{n+1})^k
\]
so
\[
  K_{1,0}u + K_{1,0}L_{0,0}K_{0,1}u \in L^2 _{\rm loc}(\bR^{n+1})^k
\]
Define
\[
  \tilde{K} = K_{11} - K_{10}L_{00}K_{01}.
\]
Then equation \ref{eqn:decomp1} can be rewritten
\begin{equation}
  \label{eqn:shs1}
  M\partial_t u_1 + \tilde{K}u_1 \in L^2_{\rm loc}(\bR^{n+1},V_1)
\end{equation}
Note that for each $t \in \bR, (\bx,\xi) \in T^*(\bR^n)$, both $V_0$ and $V_1$ are invariant subspaces of $\tilde{K}(t,\bx,\xi)$, and $V_0 \subset {\rm ker}\tilde{K}(t,\bx,\xi)$. Also, $M$ is invertible when restricted to $V_1 = {\rm Rng} M = {\rm Rng } \Pi_1$ , but not (necessarily) positive definite.

@@

Set $u=(p,v_x,v_z), \bx=x, x_2=z. \xi=\xi_x$. Then \ref{eqn:awe} takes the form \ref{eqn:shs} with
\[
  L =
  \left(
    \begin{array}{ccc}
      0 & 0 & 1\\
      0 & 0 & 0\\
      1 & 0 & 0
    \end{array}
  \right),
  M ={\rm diag}\left(\frac{1}{\kappa},\rho,\rho\right),
  A =
 \left(
    \begin{array}{ccc}
      0 & 1 & 0\\
      1 & 0 & 0\\
      0 & 0 & 0
    \end{array}
  \right),
\]
\[
  M + A\xi + L\zeta =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa} & \xi & \zeta \\
      \xi & \rho & 0 \\
      \zeta & 0 & \rho
    \end{array}
  \right)
\]
Determinant is
\[
  {\rm det} = \rho\left(\frac{\rho}{\kappa} - \xi^2 - \zeta^2\right)
\]
Therefore take $\Gamma = \{\xi: |\xi| \lt \mbox{inf
}\{\sqrt{\rho(\bx,z)/kappa(\bx,z)}, \mbox{ all } |z| < Z\}$. For $\xi
\in \Gamma$, there are two roots $\zeta = \pm \sqrt{\rho/\kappa - \xi^2}.

So $V_0={\rm span}(\{e2\}),\, V_1={\rm span}(\{e1,e3\}), \Pi_0 = {\rm diag}(0,1,0)$ 
\[
  K(t,\bx,\xi) =  A_1(\bx) \xi_1 + A_2(\bx) \xi_2 =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa(\bx)}\omega & \xi_x & 0 \\
      \xi_x & \rho(\bx) \omega & 0 \\
      0 & 0 & \rho(\bx) \omega
    \end{array}
  \right)
\]
whence $K_{0,0} = {\rm diag}(0, \rho(\bx) \omega, 0)$.
\[
  K_{1,1}(t,\bx,\xi) =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa(\bx)}\omega & 0 & 0 \\
      0 & 0 & 0 \\
      0 & 0 & \rho(\bx) \omega
    \end{array}
  \right),
\]
\[
  K_{0,1}(t,\bx,\xi) =
  \left(
    \begin{array}{ccc}
      0 & \xi_x & 0 \\
      0 & 0 & 0 \\
      0 & 0 & 0
    \end{array}
  \right)
\]
and $K_{1,0} = K_{0,1}^T$.

Choose $\omega_0>0$, $\phi \in C^{\infty}(\bR)$ so that $\phi(\omega) = 1$ for $\omega> 2\omega_0$, $=0$ for $\omega < \omega_0$. Set
\[
  L_{0,0}= {\rm diag}\left(0, \frac{\phi(|\omega|)}{\rho(\bx) \omega}, 0\right)
\]
Then $L_{0,0}K_{0,0} = I$ restricted to $V_0$ and away from zero frequency, and
\[
  \tilde{K} = K_{1,1} - K_{1,0}L_{0,0}K_{0,1} =
  \left(
    \begin{array}{ccc}
      \frac{\omega}{\kappa} - \frac{\xi_x^2\phi(|\omega|)}{\rho \omega} & 0 & 0\\
      0 & 0  & 0 \\
      0 & 0 & \rho \omega
    \end{array}
  \right).
\]
Since $V_1={\rm span}(e_1,e_3)$, the determinant of the restricted characteristic polynomial is obtained by dropping the second row and column:
\[
  \det
  \left(
    \begin{array}{cc}
      \frac{\omega}{\kappa} - \frac{\xi_x^2\phi(|\omega|)}{\rho \omega} &  \xi_z\\
      \xi_z &  \rho \omega
    \end{array}
  \right).
\]
\[
  = \frac{\rho \omega^2 }{\kappa} - \xi_x^2\phi(|\omega|) - \xi_z^2
\]
\[
  = \frac{\rho \omega^2 }{\kappa} - \xi_x^2 - \xi_z^2 \mbox{ mod }  S^{-\infty}
\]  
as expected. So a maximal choice for $\Gamma$ would be
\[
  \Gamma = \{(z,(t,x),(\omega,\xi_x)): c(z,x)|\xi_x| < |\omega|\}.
\]
\section{2D Elasticity}

@@

\subsection{PsiDO RHS}
Suppose that $K \in OPS^1$ is skew-adjoint, at least in principal part: $K_1^*=-K_1$. Then there is unitary $U \in OPS^0$ so that $U(x,\xi)^*K_1(x,\xi)U(x,\xi) = i\Lambda(x,\xi) = i\mbox{diag}(\lambda_1(x,\xi),...\lambda_k(x,\xi))$, with scalar $\lambda_j \in OPS^1, j=1,...,k$ (in fact, homogeneous of degree 1). Hence
\[
  \partial_t S(t) = -iU \Lambda U^*S(t) + RS(t), R \in OPS^0 
\]
Write $\tilde{S} = U^*SU$. Then 
\[
  \partial_t \tilde{S}(t) = -i\Lambda \tilde{S}(t) + \mbox{ mod } OPS^0 
\]
If $u^0 = (u^0_1,...,u^0_k)$, then $\tilde{u}(t) = \tilde{S}(t)u^0$ satisfies
\[
  \partial_t \tilde{u}(t) = -i\Lambda \tilde{u}(t) + ...
\]
so $\tilde{u}_i$ solves
\[
  \partial_t \tilde{u}_i(t) = -i\lambda_i \tilde{u}_i(t), \, i=1,...,k
\]
Let $\tilde{S}_i$ solve
\[
  \partial_t \tilde{S}_i(t) = - i\lambda_i \tilde{S}_i(t)
\]
Then
\[
  \tilde{u}_i(t) = \tilde{S}_i(t) u^0_i = (\tilde{S}(t)u^0)_i 
\]
whence
\[
  \tilde{S} = \mbox{diag}(\tilde{S}_1,....,\tilde{S}_k).
\]

From equation \ref{eqn:qevol1},
\[
  \tilde{Q}_i(t) = \tilde{S}_i(-t)\delta \tilde{S}_i(t)
\]
satisfies
\[
  \partial \tilde{Q}_i(t) = -i\tilde{S}_i(-t)\delta \lambda_i \tilde{S}_i(t), \, i=1,,,.k.
\]
and $\tilde{Q} = \mbox{diag}(\tilde{Q}_1,...,\tilde{Q}_k)$.
From \cite{Tay:81}, Egorov's Theorem (Section VIII.1),
\[
  \tilde{Q}_i(t; x,\xi) = -i \int_0^t ds \,\delta \lambda_i(y_i(s;x,\xi),\eta_i(s;x,\xi))
\]
in which $(y_i(s;x,\xi),\eta_i(s;x,\xi))$ is the integral curve of the Hamiltonian vector field
\[
  H_i(x,\xi) = (\partial_{\xi}\lambda_i(x,\xi), - \partial_x\lambda_i(x,\xi))
\]
with $y_i(0;x,\xi)=x, \eta_i(0;x,\xi)=\xi$.

@@

This observation implies a similar result for the H-J system
\begin{equation}
  \label{eqn:hjdef}
  0 = \partial_t u + H(t,\bx,\partial u).
\end{equation}
Replace $x$ by $(t,x)$, $F(x,\partial_x u)$ by the RHS of equation
\ref{eqn:hjdef}.  Then precisely the same results obtain, with $F$ is
replaced by $H$.

>>>>

\section{Local Analysis of Surface Source Field}
$k \times  k$ symmetric hyperbolic system: in $\bR^{n+1}$, $\Omega
\subset \bR^n, \Gamma_r, \Gamma_s \subset \partial \Omega$. $\Gamma_r$
is receiver locus, $\Gamma_s$ is sourcee locus. Assume that $\Gamma_s$
is a subset of a coordinate neighborhood in  which coordinates
$(z,\bx) \in \bR^{n-1} \times \bR$ are
chosen so that $\Gamma_i\subset \{(z,\bx): z=z_i\}, i=s,r$ with $z_s <
z_r$.

Assume $M, A_1,...,A_{n-1}, L \in C^{\infty}(\bR^n, \bR^{k\times k})$
are symmetric and $M$ is positive-definite.

Let $\chi \in C^{\infty}(\Gamma_s \times \bR, \bR^k)$.
Develop an asymptotic solution of
\begin{equation}
  \label{eqn:shs}
  (M\partial_t + \sum_{i=1}^{n-1}A_i \partial_{x_i} + L \partial_z)
  u = 0,\, u(t,z,\bx_s) = \chi(t,\bx)e^{i\omega(t + \bx \cdot \xi_0)}
\end{equation}
of the form
\begin{equation}
  \label{eqn:hfa}
  u(t,z,\bx) \approx e^{i\omega(t + \psi(z,\bx))} \sum_{n=0}^{\infty}
  (i\omega)^{-n}a^n(t,z,\bx) U^n(z,\bx)
\end{equation}
in which $a^n, n=0,...$ is scalar and $U^n, n=0,...$ is in $\bR^k$.

Substitute first term in equation \ref{eqn:shs}, obtain
\[
(M\partial_t + A\cdot \partial_x + L \partial_z)u(t,z,\bx) =
\]
\[
 e^{i\omega(t + \psi(z,\bx))}\left[ i\omega (M + A
\cdot \partial_x \psi(z,\bx) + L \partial_z
\psi(z,\bx))U(z,\bx)a^0(t,z,\bx) \right.
\]
\[
+ M(z,\bx) U^0(z,\bx) \partial_t a^0(t,z,\bx) + A(z,\bx)\cdot \partial_x
(a^0(t,z,\bx) U^0(z,\bx))
\]
\[
 \left.   + L(z,\bx)\partial_z (a^0(t,z,\bx)U^0(z,\bx))\right]
\]
\[
+  e^{i\omega(t + \psi(z,\bx))}\left[ (M + A
\cdot \partial_x \psi(z,\bx) + L \partial_z
\psi(z,\bx))U^1(z,\bx)a^1(t,z,\bx) \right.
\]
\[
  + (i\omega)^{-1} (M(z,\bx) U^1(z,\bx) \partial_t a^1(t,z,\bx)
    + A(z,\bx)\cdot \partial_x  (a^1(t,z,\bx) U^1(z,\bx))
\]
\begin{equation}
  \label{eqn:series}
  \left.   + L(z,\bx)\partial_z (a^1(t,z,\bx)U^1(z,\bx)))\right]
+...
\end{equation}

Assume $\Sigma$ is an open neighborhood of the zero section in
$T^*\Gamma_s$, so that for each $(\bx,\xi) \in \Sigma$, $|\xi|$ is
sufficiently small that $M + A\cdot \xi$ is positive
definite. Further, for $z$ sufficiently small,
there are $l$ independent solutions of 
$(\zeta_1(z,\bx,\xi),U^0_1(z,\bx,\xi)),...,(\zeta_l(z,\bx,\xi), U^0_l(z,\bx,\xi))$ of
\begin{equation}
  \label{eqn:nullsp}
 (M + A\cdot \xi + L \zeta) U^0=0, \, \zeta\ne 0.
\end{equation}
The $U^0$s are orthogonal, and might as well normalize by
$|U^0|=1$. For each $(\bx,\xi) \in \Gamma$, construct by method of characteristics solutions
$\psi_1,...,\psi_l$ of 
\begin{equation}
  \label{eqn:eik}
\partial_z \psi_i(z,\bx,\xi) = \zeta_i(z,\bx,\partial_x\psi(z,\bx,\xi))
\end{equation}
with $\psi_l(\bx,0,\xi) =\xi \cdot x$. The corresponding Hamiltonian
system for $(\bx_i(z;\bx_0,\xi_0),\xi_i(z;\bx_0,\xi_0))$ with
$(\bx_0,\xi_0) \in \Gamma$ is
\begin{equation}
  \label{eqn:zetahe1}
  \frac{d\bx_i}{dz} = - \partial_{\xi}\zeta_i(z,\bx_i,\xi_i),\,
  \bx_i(0;\bx_0,\xi_0) = \bx_0;
\end{equation}

\begin{equation}
  \label{eqn:zetahe2}
  \frac{d\xi_i}{dz}
 = \partial_x\zeta_i(z,\bx_i,\xi_i),\, \xi_i(0;\bx_0,\xi_0) = \xi_0.
\end{equation}

From the relation \ref{eqn:hsol}, 
\[
  \psi_l(\bx_i(z;\bx_0,\xi_0),z,\xi_i(z;\bx_0,\xi_0))= \bx_0\cdot\xi_0 
\]
\begin{equation}
  \label{eqn:psihe}
+ \int_{z_s}^z ds [\zeta(\bx_i(s;\bx_0,\xi_0),s, \xi(s;\bx_0,\xi_0)) - \xi(s;\bx_0,\xi_0)\cdot \partial_{\xi}\zeta_i(\bx_i(s;\bx_0,\xi_0),s,\xi_i(s;\bx_0,\xi_0))]
\end{equation}

As previously noted, $\zeta_i \ne 0$ if $\Sigma$ is chosen
sufficiently small. Enumerate the $\zeta$s so that $zeta_1,.../\zeta_m
< 0, \zeta_{m+1},...,\zeta_l > 0$. Then from the eikonal equation
\ref{eqn:eik}, the time $t$ along equal phase surfaces $t +
\psi_i(z,\bx_i(z,\bx_0,\xi_0),\xi_i(z,\bx_0,\xi_0)) = \mbox{ const}$
increases for $i=1,...,m$, decreases for $i=m+1,...,l$.

% Suppose that $supp \chi \subset \{(\bx,t): t > 0\}$.
So much for the first term in the RHS of equation
\ref{eqn:series}. The second and third terms are of order zero in
$i\omega$, hence should cancel. However the matrix in the third term
is not invertible in view of the relation \ref{eqn:nullsp}. Therefore
the second term must be orthogonal to the kernel of this matrix, which
since the matrix is symmetric simply means in its orthogonal to $U^0$.
That is,
\[
U^0(z,\bx) \cdot (M(z,\bx) U^0(z,\bx) \partial_t a^0(t,z,\bx) + A(z,\bx)\cdot \partial_x
(a^0(t,z,\bx) U^0(z,\bx))
\]
\[+ L(z,\bx)\partial_z
  (a^0(t,z,\bx)U^0(z,\bx))) = 0,
\]
or
\[
 (b_t \partial_t + b_x \cdot \partial_x + b_z \partial_z)
 a^0 + c a^0 = 0
\]
where
\[
  b_t = U^0 \cdot M U^0, b_{x,i} = U^0 \cdot A_i U^0, b_z = U^0 \cdot
  L U_0
\]
and $c$ is the rest, not involving derivatives of $a^0$.

@@

Set $u=(p,v_x,v_z), \bx=x, x_2=z. \xi=\xi_x$. Then \ref{eqn:awe} takes the form \ref{eqn:shs} with
\[
  L =
  \left(
    \begin{array}{ccc}
      0 & 0 & 1\\
      0 & 0 & 0\\
      1 & 0 & 0
    \end{array}
  \right),
  M ={\rm diag}\left(\frac{1}{\kappa},\rho,\rho\right),
  A =
 \left(
    \begin{array}{ccc}
      0 & 1 & 0\\
      1 & 0 & 0\\
      0 & 0 & 0
    \end{array}
  \right),
\]
\[
  M + A\xi + L\zeta =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa} & \xi & \zeta \\
      \xi & \rho & 0 \\
      \zeta & 0 & \rho
    \end{array}
  \right)
\]
Determinant is
\[
  {\rm det} = \rho\left(\frac{\rho}{\kappa} - \xi^2 - \zeta^2\right)
\]
Therefore choose $\epsilon > 0$ and define $\Gamma = \{(\bx,\xi): |\xi| < \mbox{ inf}\{\sqrt{\rho(\bx,0)/\kappa(\bx,0)}, \mbox{ all } |z| < Z\}$. For $\xi
\in \Gamma$, there are two roots $\zeta_{\pm} = \pm \sqrt{\rho/\kappa - \xi^2}.$
Accordingly there are two solutions of equation \ref{eqn:eik},
\[
  \psi_{\pm}(\bx_{\pm}(z;\bx_0,\xi_0),z,\xi_{\pm}(z;\bx_0,\xi_0))= \bx_0\cdot\xi_0
\]
\[
 +\int_0^z ds \zeta_{\pm}(\bx_{\pm}(s;\bx_0,\xi_0),s,\xi_{\pm}(s;\bx_0,\xi_0))-\xi_{\pm}(s;\bx_0,\xi_0)\cdot \partial_{\xi}\zeta_{\pm}(\bx_{\pm}(s;\bx_0,\xi_0),s,\xi_{\pm}(s;\bx_0,\xi_0))
\]
\[
  =\bx_0 \cdot \xi_0 \pm \int_0^z
  \frac{ds}{c(\bx_{\pm}(s;\bx_0,\xi_0),z)
    \sqrt{(1-\xi_{\pm}(s;\bx_0,\xi_0),z)^2
    c(\bx_{\pm}(s;\bx_0,\xi_0),z)^2}}
\]
where $c = \sqrt{\kappa/\rho}$ is the sound velocity.

\section{2D Elasticity}

@@

\subsection{PsiDO RHS}
Suppose that $K \in OPS^1$ is skew-adjoint, at least in principal
part: $K_1^*=-K_1$. Then there is unitary $U \in OPS^0$ so that
$U(x,\xi)^*K_1(x,\xi)U(x,\xi) = i\Lambda(x,\xi) =
i\mbox{diag}(\lambda_1(x,\xi),...\lambda_k(x,\xi))$, with scalar
$\lambda_j \in OPS^1, j=1,...,k$ (in fact, homogeneous of degree
1). Also,
\begin{equation}
  \label{eqn:ortho}
  U(x,D)^*U(x,D) = U(x,d)U(x,D)^* = I \mbox{ mod } OPS^{-1}
\end{equation}
Define $S(t)$ to be the one-parameter group satisfying
\[
  \partial_t S(t) = -K S(t), S(0)=I
\]
Note that $S(-t)$ is inverse to $S(t)$, and 
\[
  \partial_t S(-t) = -S(-t) \partial_t S(t) S(-t) = S(-t)K
\]
Hence
\[
  \partial_t S(t) = -iU \Lambda U^*S(t) + RS(t), R \in OPS^0 
\]
Write $\tilde{S} = U^*SU$. Then 
\[
  \partial_t \tilde{S}(t) = -i\Lambda \tilde{S}(t) + \mbox{ mod } OPS^0 
\]
If $u^0 = (u^0_1,...,u^0_k)$, then $\tilde{u}(t) = \tilde{S}(t)u^0$ satisfies
\[
  \partial_t \tilde{u}(t) = -i\Lambda \tilde{u}(t) + ...
\]
so $\tilde{u}_i$ solves
\[
  \partial_t \tilde{u}_i(t) = -i\lambda_i \tilde{u}_i(t), \, i=1,...,k
\]
Let $\tilde{S}_i$ solve
\begin{equation}
  \label{eqn:stilde}
  \partial_t \tilde{S}_i(t) = - i\lambda_i \tilde{S}_i(t)
\end{equation}
Then
\[
  \tilde{u}_i(t) = \tilde{S}_i(t) u^0_i = (\tilde{S}(t)u^0)_i 
\]
whence
\[
  \tilde{S} = \mbox{diag}(\tilde{S}_1,....,\tilde{S}_k).
\]
and
\begin{equation}
  \label{eqn:spec}
  S(t) = \sum_{i=1}^k U_i \tilde{S}_i(t)U_i^*
\end{equation}

Define
\[
  F = \phi_r S(T) \phi_s
\]
in which $\phi_,r \in C_0^{\infty}(\bR^{n+1})$ and $T>0$. Suppose that $K$
is perturbed by $\delta K \in OPS^1$, also essentially skew. Then
$\Lambda$, $U$, $S$, $\tilde{S}$ and $F$ undergo perturbations
$\delta \Lambda$, $\delta U$, $\delta S$, $\delta \tilde{S}$, and
$\delta F$. Our object is to understand the structure of $\delta F$, under the
assumption that $\phi_r \delta K \in OPS^{-\infty}$.

This assumption on $\delta K$ implies that $\phi_r \delta U \in
OPS^{-\infty}$. 
\[
  \delta F =  \phi_r \delta S(T)  = \phi_r \left(\sum _{j=1}^k \delta U_j \tilde{S}_j(T) U_j^*
\right.
\]
\[
 +  \left. \sum_{j=1}^k U_j \delta\tilde{S}_j(T)U_j^* + \sum_{J=1}^k U_j
    \tilde{S}_j(T)\delta U_j^*\right) 
\]
Every term in the first sum on the RHS is bounded $H^s \rightarrow H^{s-1}$ since
$\phi_r \delta U_i \in OPS^{-\infty}$.  Since $[\phi_rU_i], \in OPS^{-1}$, 
\[
  \phi_r  U_j \delta \tilde{S}_j(T)  U_j^*  = U_j \phi_r
  \tilde{S}_j(T) U_j^*
  +...
\]
where the elided terms are operators mapping $H^s$ to $H^{s-1}$, any
$s$. So,
\[
 \delta F = \sum_{j=1}^k U_j \phi_r \left( \delta\tilde{S}_j(T) U_i^*
   + \tilde{S}_j(T) \delta U_j^*\right)
  + ...
\]
and
\[
 S(-T)\delta F =\left(\sum_{i=1}^k U_i \tilde{S}_i(T)
    U_i^*\right) \left(\sum_{j=1}^k U_j \phi_r ( \delta\tilde{S}_j(T) U_i^*
    + \tilde{S}_j(T) \delta U_j^*)\right)
\]  
Using the relation \ref{eqn:ortho},
The first order perturbation of the definition \ref{eqn:stilde} is
\begin{equation}
  \label{eqn:dstilde}
  \partial_t \delta \tilde{S}_i(t) = - i\lambda_i \delta
  \tilde{S}_i(t) - i\delta \lambda_i \tilde{S}_i(t)
\end{equation}
Since $\tilde{S_i}(-t)$ is inverse to $\tilde{S}_i(t)$,
\[
  \partial_t \tilde{S}_i(-t)= -\tilde{S}_i(-t) (\partial_t \tilde{S}_i(t)) \tilde{S}_i(-t)
\]
\begin{equation}
  \label{eqn:stildeinv}
= -\tilde{S}_i(-t)(-i\lambda_i \tilde{S}_i(t)) \tilde{S}_i(-t) = i\tilde{S}_i(-t)\lambda_i 
\end{equation}
So
%\[
% \partial_t (\tilde{S}_i(-t) \phi_r \delta \tilde{S}_i(t) \phi_s) 
%\]
%\[
%  = i\tilde{S}_i(-t)\lambda_i \phi_r \delta \tilde{S}_i(t) \phi_s +
%  \tilde{S}_i(-t) \phi_r (- i\lambda_i \delta
%  \tilde{S}_i(t) - i\delta \lambda_i \tilde{S}_i(t)) \phi_s
%\]
%\[
%  = -i\tilde{S}_i(-t)[\lambda_i,\phi_r] \delta \tilde{S}(t) \phi_s -i
%  \tilde{S}_i(-t)\phi_r\delta\lambda_i\tilde{S}_i(t) \phi_s
%\]
%\begin{equation}
%  \label{eqn:qevol1}
%  = -i\tilde{S}_i(-t)[\lambda_i,\phi_r]\tilde{S}_i(t) \tilde{S}_i(-t)\delta \tilde{S}(t) \phi_s %-i
%  \tilde{S}_i(-t)\phi_r\delta\lambda_i\tilde{S}_i(t) \phi_s.
%\end{equation}
%Similarly,
\begin{equation}
  \label{eqn:dstildeconj}
  \partial_t\tilde{S}_i(-t)\delta \tilde{S}_i(t) = -i\tilde{S}_i(-t)\delta \lambda_i \tilde{S}_i(t).
\end{equation}
From \cite{Tay:81}, Egorov's Theorem (Section VIII.1), for $p \in OPS^s(\bR^n)$,
\begin{equation}
  \label{eqn:egorov}
   \tilde{S}_i(-t) p \tilde{S}_i(t)=  p \circ C_i(t),\, p\tilde{S}_i(t) =
   \tilde{S}_i(t)p \circ C_i(t)
\end{equation}
in which $C_i$ is the one-paraimeter family of symplectic maps given by
\begin{equation}
  \label{eqn:canon}
  C_i(t)(x,\xi)=(y_i(t;x,\xi),\eta_i(t;x,\xi))
\end{equation}
Here $t \rightarrow y_i(t;x,\xi),\eta_i(t;x,\xi) $is the integral curve of the
Hamiltonian vector field
\[
  H_i(x,\xi) = (\partial_{\xi}\lambda_i(x,\xi), - \partial_x\lambda_i(x,\xi))
\]
with $y_i(0;x,\xi)=x, \eta_i(0;x,\xi)=\xi$.

For $p \in OPS^{\infty}$, define
\[
  \Gamma_i[p] = \int_0^T dt \, p \circ C_i(t)
\]
Then from the identity \ref{eqn:dstildeconj} follows
\[
  \delta\tilde{S}_i(T) = \tilde{S}_i(T) \Gamma_i[ -i \delta \lambda_i]
\] 
so
\[
  \delta F = \sum_{i=1}^k U_i \phi_r \delta \tilde{S}_i \phi_s U_i^*
\]
\[
  =\sum_{i=1}^k U_i \phi_r \tilde{S}_i(T) \Gamma_i[ -i \delta \lambda_i]\phi_s U_i^*
\]
\[
 Q = -i\sum_{i=1}^k U_i \tilde{S}_i(-T) \phi_r \tilde{S}_i(T) \Gamma_i[\delta \lambda_i] U_i^*\phi_s
  + ...
\]
\[
  = -i \sum_{i=1}^k U_i (\Gamma_i[\phi_r] \Gamma_i[\delta \lambda_i] )
  U_i^*
\]

The right hand side of equation \ref{eqn:qevol1} contains three
expressions of the form appearing on the LHS of \ref{eqn:egorov}.

@@

This observation implies a similar result for the H-J system
\begin{equation}
  \label{eqn:hjdef}
  0 = \partial_t u + H(t,\bx,\partial u).
\end{equation}
Set $X=(t,x)$, $P=(q,p)$ (with $q$ dual to $t$, $F(X,\partial_X u) =
\partial_t u + H(t,x,\partial_x u)$, so the Hamiltonian is $F(X,P) =
q+H(t,x.p)$.  Thus
\begin{eqnarray*}
  \frac{dt}{ds} & = & \partial_q F = 1 \\
  \frac{dx}{ds} & = & \partial_p F = \partial_p H \\
  \frac{dq}{ds} & = & -\partial_t F = -\partial_t H \\
  \frac{dp}{ds} & = & -\partial_x F = -\partial_x H
\end{eqnarray*}
From the first equation, $t=s$ up to a constant shift. From the third,
\[
  q(t) = -\int_0^t ds \partial_tH(s,x(s),p(s))
\]
\[
  = -\int_0^t ds \frac{d}{ds}H(s,x(s),p(s)) - \frac{dx}{ds}(s)\cdot
  \partial_x H(s,x(s),p(s)) -\frac{dp}{ds}(s)\cdot \partial_p
  H(s,x(s),p(s))
\]
\[
  = -H(t,x(t),p(t)) + H(0,x(0),p(0))
\]
in view of the 2nd and 4th equations.
Note that these are the Hamiltonian system with Hamiltonian $H$.

The result \ref{eqn:sol} becomes
\begin{equation}
  \label{eqn:hsol}
  u(t,x(t))=u(0,x(0)) +tH(0,x(0),p(0))+ \int_0^t ds (-H(s,x(s),p(s)) + p(s)\cdot (\partial_p H)(s,x(s),p(s))).
\end{equation}

% Suppose that $\Gamma_0, \Gamma \subset T^*(\bR^n)$ are conic open sets with $\overbar{\Gamma_0 \subset \Gamma$ and $\delta t >0$. Assume that  that for $|t|\le \delta t$ and $(\bx,\xi) \in Gamma$, $K_{00}(0,\bx,\xi)$ is invertible as a map $V_0 \rightarrow V_0$.
Let  $L_{00}(t,\bx,\xi) \in C^{\infty}(\bR, S^{-1}(\bR^n))$ be inverse to $K_{0,0}(t,\bx,\xi)$ on $V_0$: that is,
\[
  K_{0,0}(t,\bx,\xi)L_{0,0}(t,\bx,\xi) v=v=L_{0,0}(t,\bx,\xi)K_{0,0}(t,\bx,\xi)v
\]
for all $v \in V_0$. Construct $L_{0,0}$ to be homogeneous of degree -1 outside of a neighborhood of $\xi=0$, with $V_1$ an invariant subspace for $L_{0,0}(t,\bx,\xi)$ on which it vanishes. It follows that $L_{0,0}$ is symmetric, and that
\[
  \Pi_0 u - L_{0,0}K_{0,0}\Pi_u = \Pi_0 u - L_{0,0}K_{0,0}u = \Pi_0 u + L_{0,0}K_{0,1}u \in H^{1}_{\rm loc}(\bR^{n+1})^k
\]
so
\[
  K_{1,0}u + K_{1,0}L_{0,0}K_{0,1}u \in L^2 _{\rm loc}(\bR^{n+1})^k
\]
Define
\[
  \tilde{K} = K_{11} - K_{10}L_{00}K_{01}.
\]
Then equation \ref{eqn:decomp1} can be rewritten
\begin{equation}
  \label{eqn:shs1}
  M\partial_t u_1 + \tilde{K}u_1 \in L^2_{\rm loc}(\bR^{n+1},V_1)
\end{equation}
